Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-23 paper.tex
cite well

Before turning to the definition of the abstract data types, we first
give the definition of values and cast results used by the \effCEK{C}, as they 
are mentioned in the definition of the ADTs. The notation $\hcvOOinj{P}{v}$ 
stands for values that are cast to the dynamic type, as in ...

\todo[inline]{The notation $\hcvOOinj{P}{v}$ is non-standard
   and should be explained. -JS
\\---\\
I switch to the standard notation because we have an observation $\oOOinj$
But I forget the origin of this notation, can Jeremy cite it?
 -KC}

>>>>

Before turning to the definition of the abstract data types, we first
give the definition of values and cast results used by the \effCEK{C}, as they 
are mentioned in the definition of the ADTs. The $\hcvOOinj{P}{v}$ stands for 
values that are cast to the dynamic type, as in \citet{wadler2009well}.

\todo[inline]{The notation $\hcvOOinj{P}{v}$ is non-standard
   and should be explained. -JS
\\---\\
Fixed. -KC}
